Note on: Out-of-Sample Error for Laplacian Eigenmaps

### 2021-03-07 notes/weekly_notes/12.24.20.NotesForWeek.tex
Added first part of kernel smoothing bias.

For a kernel function $\eta(\cdot): [0,\infty) \to (-\infty,+\infty)$, bandwidth $\varepsilon > 0$, and a distribution $Q$, the \emph{Nadaraya-Watson kernel smoother} $T_{\varepsilon,Q}$ is given by
\begin{equation*}
\bigl(T_{\varepsilon,Q}f)(x) := \frac{1}{d_Q(x)} \int_{\Omega} f(z)\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dQ(z)
\end{equation*}
where $d_Q(x) = \int_{\Omega} \eta\bigl(\|z - x\|/\varepsilon\bigr) \,dQ(z)$. We denote $T_{\varepsilon,P_n}$ by $T_{\varepsilon,n}$, and $d_{P_n}$ by $d_n$. For convenience, we will assume that $\eta$ is normalized, $\int_{0}^{\infty} \eta(s) \,ds = 1$, and we will denote $K(\cdot) = (\eta(\cdot))^2$.

The estimated function $\wh{f}$ we will consider is a kernel smoother passed over $\wh{\theta}$,
\begin{equation}
\label{eqn:kernel_smoother_laplacian_eigenmaps}
\wh{f}(x) := T_{\varepsilon,n}\wh{\theta}_{1:n}(x).
\end{equation}
In order to relate the out-of-sample error $\|\wh{f} - f^{\ast}\|_P$ to the in-sample error $\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n$, we will assume the following.
\begin{enumerate}[label=(A\arabic*)]
	\item
	\label{asmp:kernel}
	The kernel function $\eta$ is supported on a subset of $[0,1]$, with $\eta(1/2) > 0$. Additionally, $\eta$ is \textcolor{red}{Lipschitz} on its support.
	\item 
	\label{asmp:domain} There exists $\alpha > 0$ such that for every $x \in \mc{X}$, $d_{\nu}(x) \geq \alpha \cdot \varepsilon^d$.
	\item 
	\label{asmp:density}The distribution $P$ admits a density $p$ with respect to Lebesgue measure. The density $p \in C^1(\mc{X})$, and is bounded away from $0$ and $\infty$ for all $x \in \mc{X}$,
	\begin{equation*}
	0 < p_{\min} \leq p(x) < p_{\max} < \infty.
	\end{equation*}
\end{enumerate}
Under Assumption~\ref{asmp:kernel}, we automatically have that $d_\nu(x) = \varepsilon^d$ for all $x \in \mc{X}_{\varepsilon}$. Assumption~\ref{asmp:domain} is thus a condition on the boundary $\partial \Omega$, and is implied for all sufficiently small $\varepsilon$ if the boundary is Lipschitz. 
\begin{lemma}
	\label{lem:kernel_smoothing_laplacian_eigenmaps}
	Suppose $f^{\ast} \in H^1(\mc{X})$ and $p \in C^1(\mc{X})$. Then with probability at least $1 - \delta - C\varepsilon^d\exp\{-Cn\varepsilon^d\}$, it holds that
	\begin{equation*}
	\|\wh{f} - f^{\ast}\|_P^2 \leq C\biggl(\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n^2 + \frac{1}{\delta} \cdot \frac{\varepsilon^2}{n\varepsilon^d} |f|_{H^1(\mc{X})}^2 + \frac{1}{\delta}\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2\biggr)
	\end{equation*}
\end{lemma}
Notice that the variance term in the above is smaller than the typical variance term for kernel smoothing of noisy data (on the order of $1/(n\varepsilon^d)$) by a factor of $\varepsilon^2$. The bias term, on the other hand, is standard (at least when $f^{\ast} \in C_0^s(\Omega)$). In particular the following estimate of the bias can be obtained. 
\begin{lemma}
	\label{lem:kernel_smoothing_bias}
	Suppose $f^{\ast} \in H_0^{s}(\Omega)$, $p \in C^{r}(\Omega)$ for $r = s - 1$, and that $\eta$ is an order-$s$ kernel. It follows that
	\begin{equation*}
	\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2 \leq C \varepsilon^{2s}.
	\end{equation*}
\end{lemma}
\begin{proof}[Proof (when dimension $d = 1$).]
\end{proof}

@@

	\textit{Proof of \eqref{pf:kernel_smoothing_laplacian_eigenmaps_0}.} We will begin by assuming that $\eta(z) \geq 0$ for all $z$, and return to prove the claim in its full generality at the end.

	The left hand side of~\eqref{pf:kernel_smoothing_laplacian_eigenmaps_0} is equal to $\|T_{\varepsilon,n}(\wh{\theta}_{1:n} - f^{\ast}_{1:n})\|_P$, and~\eqref{pf:kernel_smoothing_laplacian_eigenmaps_0} is implied by showing that the operator $T_{\varepsilon,n}: L^2(X) \to L^2(\Omega)$ is (up to a constant) a contraction, meaning that for any $u \in L^2(X)$,
	\begin{equation}
	\label{pf:kernel_smoothing_laplacian_eigenmaps_1}
	\|T_{\varepsilon,n}u\|_P^2 \leq \frac{1}{\alpha}\bigl(1 + o_P(1)\bigr) \|u\|_n^2.
	\end{equation}
	We begin with a pointwise estimate, which follows from Jensen's inequality:
	\begin{equation*}
	\Bigl(\bigl(T_{n,\varepsilon}u\bigr)(x)\Bigr)^2 \leq \frac{1}{d_n(x) n} \sum_{i = 1}^{n} \bigl(u(X_i)\bigr)^2 \eta\biggl(\frac{\|X_i - x\|}{\varepsilon}\biggr).
	\end{equation*}
	(Note that it is here that we have used the positivity of $\eta(\cdot)$.) Integrating with respect to $P$ and exchanging sum with integral yields an upper bound on the $L^2(P)$ norm of $T_{n,\varepsilon}u$,
	\begin{equation}
	\label{pf:kernel_smoothing_laplacian_eigenmaps_2}
	\|T_{n,\varepsilon}u\|_P^2 \leq \sum_{i = 1}^{n} u_i^2 \Bigl(\int_{\Omega} \frac{\eta(\|X_i - x\|/\varepsilon)}{n d_n(x)} p(x) \,dx \Bigr)
	\end{equation}
	The degree estimate $d_n(x)$ is quite close to $p(x)$. As we show in Lemma~\ref{lem:measure_of_ball_estimate}, if $\varepsilon = \omega((\log n/n)^{1/d})$ then the empirical measure $d_n(x)$ concentrates around $d_P(x)$ uniformly over $x \in \Omega$, 
	\begin{equation*}
	\sup_{x \in \Omega}|d_n(x) - d_P(x)| = o_P(\varepsilon^d);
	\end{equation*}
	moreover, it follows from Lipschitz continuity of $p$ that for any $x \in \Omega$,
	\begin{equation*}
	d_P(x) = \int_{\Omega} \eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) p(x') \,dx' = p(x) d_{\nu}(x) + O(\varepsilon^{d + 1});
	\end{equation*}
	and thus by the triangle inequality $\sup_{x \in \Omega}|d_n(x) - d_\nu(x) p(x)| = o_P(\varepsilon^d)$.

@@

\section{Miscellaneous}
I put things here which did not belong in any other section.

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_bias}, $d = 1$ and $p$ uniform}
Without loss of generality take the domain $\Omega = (0,1)$. Recall that we are interested in upper bounding
\begin{equation*}
\|T_{P,\varepsilon}u - u\|_{P}^2 = \int_{\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x) \leq C\varepsilon^{2k}
\end{equation*}
where $L_{P,\varepsilon}$ is a non-local approximation to the continuum weighted Laplacian, given by
\begin{equation*}
L_{P,\varepsilon}u(x) := \frac{1}{d_P(x)}\int_{\Omega} \bigl(u(z) - u(x)\bigr) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dP(z).
\end{equation*}
We begin with a pointwise analysis of $L_{p,\varepsilon}u(x)$ at a given $x \in \Omega$. We may assume without loss of generality that $u \in C_0^{\infty}(\Omega)$, since $C_0^{\infty}(\Omega)$ is dense in $H_0^k(\Omega)$ and $\|T_{P,\varepsilon}u - u\|_P^2$ is continuous with respect to $\|\cdot\|_{H_0^k}$. Since $u$ is smooth, for every $x,z \in \Omega$, we have the $k$th-order Taylor expansion
\begin{equation*}
u(z) - u(x) = \sum_{j = 1}^{k - 1} (z - x)^{j} u^{(j)}(x)  + \frac{(z - x)^k}{(k - 1)!}\int_{0}^{1}(1 - t)^{k - 1}u^{(k)}(x + t(z - x))\,dt.
\end{equation*}
As a result,
\begin{equation}
\label{pf:kernel_smoothing_bias_1d_1}
\begin{aligned}
L_{P,\varepsilon}u(x) = \frac{1}{d_P(x)} & \Biggl\{\sum_{j = 1}^{k - 1} u^{(j)}(x) \int_{\Omega}(z - x)^{j}\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr)\,dz + \\ 
& \frac{1}{(k - 1)!} \int_{\Omega} \int_{0}^{1} (1 - t)^k (z - x)^k u^{(k)}(x + t(z - x)) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dt \,dz \Biggr\}
\end{aligned}
\end{equation}
The way in which we use~\eqref{pf:kernel_smoothing_bias_1d_1} will depend on whether $x \in \Omega$ satisfies $B(x,\varepsilon) \subset \Omega$ or not. Let $\Omega_{\varepsilon} := \{x: B(x,\varepsilon) \in \Omega\}$ and let $\partial_{\varepsilon}\Omega := \Omega \setminus \Omega_{\varepsilon}$. Clearly
\begin{equation*}
\|L_{P,\varepsilon}u\|_{P}^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2}
\end{equation*}
and we now separately upper bound $I_1$ and $I_2$.

\paragraph{Upper bound on $I_1$.}
If $x \in \Omega_{\varepsilon}$ then all $z \in B(x,\varepsilon)$ also belong to $\Omega$. For one thing, this implies
\begin{equation*}
d_P(x) = \int_{\Omega} \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz = \varepsilon \cdot \int_{B(0,1)}  \eta(v) \,dv = \epsilon.
\end{equation*}
Addtionally, we have that all $j = 1,\ldots,k - 1$, 
\begin{equation*}
\int_{\Omega}(z - x)^{k}\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz = \varepsilon^j \cdot \int_{B(0,1)} v^j \eta(v) \,dv = 0,
\end{equation*}
where the second equality follows because $\eta$ is a $k$th-order kernel. Consequently $L_{P,\varepsilon}$ depends only on the $k$th derivative of $u$: changing variables to $v = (z - x)/\varepsilon$, we have
\begin{align*}
L_{P,\varepsilon}u(x) & = \frac{1}{\varepsilon} \cdot \frac{1}{(k - 1)!} \int_{0}^{1} \int_{\Omega} (1 - t)^k (z - x)^k u^{(k)}(x + t(z - x)) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz \,dv \\
& = \frac{\varepsilon^{k}}{(k - 1)!} \int_{0}^{1} \int_{B(0,1)} (1 - t)^k v^k u^{(k)}(x + t\varepsilon v) \eta(v) \,dv \,dt.
\end{align*} 
This identity along with Jensen's inequality implies that
\begin{equation*}
\Bigl(L_{P,\varepsilon}u(x)\Bigr)^2 \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \cdot  \int_{0}^{1} \int_{B(0,1)} v^{2k} \bigl(u^{(k)}(x + t\varepsilon v)\bigr)^2 \eta(|v|) \,dv \,dt.
\end{equation*}
Integrating over all $x \in \Omega_{\varepsilon}$ gives an upper bound on $I_1$. 
From here, by changing the order of integration, substituting $\wt{x} = x + t\varepsilon v$, and noting that $\wt{x} \in \Omega$, we arrive at the desired bound:
\begin{align*}
I_1 & \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \int_{0}^{1} \int_{B(0,1)} \int_{\Omega_{\varepsilon}} v^{2k} \bigl(u^{(k)}(x + t\varepsilon v)\bigr)^2 \eta(|v|) \,dx \,dv \,dt \\
& \leq \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 \int_{0}^{1} \int_{B(0,1)} \int_{\Omega} v^{2k} \bigl(u^{(k)}(\wt{x})\bigr)^2 \eta(|v|) \,d\wt{x} \,dv \,dt \\
& = \biggl(\frac{\varepsilon^{k}}{(k - 1)!}\biggr)^2 |u|_{H^k(\Omega)}^2 \sigma_{\eta}.
\end{align*}

\paragraph{Upper bound on $I_2$.}

>>>>

For a kernel function $\eta(\cdot): [0,\infty) \to (-\infty,+\infty)$, bandwidth $\varepsilon > 0$, and a distribution $Q$, the \emph{Nadaraya-Watson kernel smoother} $T_{\varepsilon,Q}$ is given by
\begin{equation*}
\bigl(T_{\varepsilon,Q}f)(x) := \frac{1}{d_Q(x)} \int_{\Omega} f(z)\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dQ(z)
\end{equation*}
where $d_Q(x) = \int_{\Omega} \eta\bigl(\|z - x\|/\varepsilon\bigr) \,dQ(z)$. We denote $T_{\varepsilon,P_n}$ by $T_{\varepsilon,n}$, and $d_{P_n}$ by $d_n$.

The estimated function $\wh{f}$ we will consider is a kernel smoother passed over $\wh{\theta}$,
\begin{equation}
\label{eqn:kernel_smoother_laplacian_eigenmaps}
\wh{f}(x) := T_{\varepsilon,n}\wh{\theta}_{1:n}(x).
\end{equation}
In order to relate the out-of-sample error $\|\wh{f} - f^{\ast}\|_P$ to the in-sample error $\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n$, we will assume the following.
\begin{enumerate}[label=(A\arabic*)]
	\item
	\label{asmp:kernel}
	The kernel function $\eta$ is compactly supported on a subset of $[0,1]$. Additionally, $\eta$ is Lipschitz on its support. Finally, for convenience we will assume that $\eta$ is normalized, 
	\begin{equation*}
	\int_{0}^{\infty} \eta(s) \,ds = 1.
	\end{equation*}
	\item 
	\label{asmp:domain} There exists $\alpha > 0$ such that for every $x \in \mc{X}$, $d_{\nu}(x) \geq \alpha \cdot \varepsilon^d$.
	\item 
	\label{asmp:density}The distribution $P$ admits a density $p$ with respect to Lebesgue measure. The density $p \in C^1(\mc{X})$, and is bounded away from $0$ and $\infty$ for all $x \in \mc{X}$,
	\begin{equation*}
	0 < p_{\min} \leq p(x) < p_{\max} < \infty.
	\end{equation*}
\end{enumerate}
Under Assumption~\ref{asmp:kernel}, we automatically have that $d_\nu(x) = \varepsilon^d$ for all $x \in \mc{X}_{\varepsilon}$. Assumption~\ref{asmp:domain} is thus a condition on the boundary $\partial \Omega$, and is implied for all sufficiently small $\varepsilon$ if the boundary is Lipschitz. Denoting $K(\cdot) = (\eta(\cdot))^2$, we note that Assumption~\ref{asmp:kernel} implies that $\eta$ is square-integrable, $\int_{0}^{\infty} K(s) \,ds < \infty$.
\begin{lemma}
	\label{lem:kernel_smoothing_laplacian_eigenmaps}
	Suppose $f^{\ast} \in H^1(\mc{X})$ and $p \in C^1(\mc{X})$. Then with probability at least $1 - \delta - C\varepsilon^d\exp\{-Cn\varepsilon^d\}$, it holds that
	\begin{equation*}
	\|\wh{f} - f^{\ast}\|_P^2 \leq C\biggl(\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n^2 + \frac{1}{\delta} \cdot \frac{\varepsilon^2}{n\varepsilon^d} |f|_{H^1(\mc{X})}^2 + \frac{1}{\delta}\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2\biggr)
	\end{equation*}
\end{lemma}
Notice that the variance term in the above is smaller than the typical variance term for kernel smoothing of noisy data (on the order of $1/(n\varepsilon^d)$) by a factor of $\varepsilon^2$. The bias term, on the other hand, is standard (at least when $f^{\ast} \in C_0^s(\Omega)$). In particular the following estimate of the bias can be obtained. 
\begin{lemma}
	\label{lem:kernel_smoothing_bias}
	Suppose $f^{\ast} \in H_0^{s}(\Omega)$, $p \in C^{r}(\Omega)$ for $r = s - 1$, and that $\eta$ is an order-$s$ kernel. It follows that
	\begin{equation*}
	\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2 \leq C \varepsilon^{2s}.
	\end{equation*}
\end{lemma}
\begin{proof}[Proof (when dimension $d = 1$).]
	\textcolor{red}{(TODO)}
\end{proof}

@@

	\textit{Proof of \eqref{pf:kernel_smoothing_laplacian_eigenmaps_0}.} We will begin by assuming that $\eta$ is positive, $\eta(z) \geq 0$ for all $z$, and return to prove the claim in its full generality at the end.

	The left hand side of~\eqref{pf:kernel_smoothing_laplacian_eigenmaps_0} is equal to $\|T_{\varepsilon,n}(\wh{\theta}_{1:n} - f^{\ast}_{1:n})\|_P$, and~\eqref{pf:kernel_smoothing_laplacian_eigenmaps_0} is implied by showing that the operator $T_{\varepsilon,n}: L^2(X) \to L^2(\Omega)$ is (up to a constant) a contraction. We will show that for any $u \in L^2(X)$,
	\begin{equation}
	\label{pf:kernel_smoothing_laplacian_eigenmaps_1}
	\|T_{\varepsilon,n}u\|_P^2 \leq \frac{1}{\alpha}\bigl(1 + o_P(1)\bigr) \|u\|_n^2.
	\end{equation}
	We begin with a pointwise estimate, which follows from Jensen's inequality:
	\begin{equation*}
	\Bigl(\bigl(T_{n,\varepsilon}u\bigr)(x)\Bigr)^2 \leq \frac{1}{d_n(x) n} \sum_{i = 1}^{n} \bigl(u(X_i)\bigr)^2 \eta\biggl(\frac{\|X_i - x\|}{\varepsilon}\biggr).
	\end{equation*}
	(Note that it is here that we have used the positivity of $\eta(\cdot)$.) Integrating with respect to $P$ and exchanging sum with integral yields an upper bound on the $L^2(P)$ norm of $T_{n,\varepsilon}u$,
	\begin{equation}
	\label{pf:kernel_smoothing_laplacian_eigenmaps_2}
	\|T_{n,\varepsilon}u\|_P^2 \leq \sum_{i = 1}^{n} u_i^2 \Bigl(\int_{\Omega} \frac{\eta(\|X_i - x\|/\varepsilon)}{n d_n(x)} p(x) \,dx \Bigr)
	\end{equation}
	The degree estimate $d_n(x)$ is quite close to $p(x)$. As we show in Lemma~\ref{lem:measure_of_ball_estimate}, if $\varepsilon = \omega((\log n/n)^{1/d})$ then the empirical measure $d_n(x)$ concentrates around $d_P(x)$ uniformly over $x \in \Omega$, 
	\begin{equation*}
	\sup_{x \in \Omega}|d_n(x) - d_P(x)| = o_P(\varepsilon^d).
	\end{equation*}
	Moreover, it follows from the Lipschitz continuity of $p$ that for any $x \in \Omega$,
	\begin{equation*}
	d_P(x) = \int_{\Omega} \eta\biggl(\frac{\|x' - x\|}{\varepsilon}\biggr) p(x') \,dx' = p(x) d_{\nu}(x) + O(\varepsilon^{d + 1}),
	\end{equation*}
	and thus by the triangle inequality $\sup_{x \in \Omega}|d_n(x) - d_\nu(x) p(x)| = o_P(\varepsilon^d)$.

@@

\section{Miscellaneous}
I put things here which do not belong in any other section.

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_bias}, $d = 1$ and $p$ uniform}
\label{subsec:kernel_smoothing_bias_pf_1d_uniform_p}
Without loss of generality take the domain $\Omega = (0,1)$. Recall that we are interested in upper bounding
\begin{equation*}
\|T_{P,\varepsilon}u - u\|_{P}^2 = \int_{\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x) \leq C\varepsilon^{2k}
\end{equation*}
where $L_{P,\varepsilon}$ is a non-local approximation to the continuum weighted Laplacian, given by
\begin{equation*}
L_{P,\varepsilon}u(x) := \frac{1}{d_P(x)}\int_{\Omega} \bigl(u(z) - u(x)\bigr) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dP(z).
\end{equation*}
Let $\Omega_{\varepsilon} := \{x: B(x,\varepsilon) \in \Omega\}$ and let $\partial_{\varepsilon}\Omega := \Omega \setminus \Omega_{\varepsilon}$. Clearly
\begin{equation*}
\|L_{P,\varepsilon}u\|_{P}^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2}
\end{equation*}
and we now separately upper bound $I_1$ and $I_2$.

\paragraph{Upper bound on $I_1$.}
We begin with a pointwise analysis of $L_{p,\varepsilon}u(x)$ at a given $x \in \Omega_{\varepsilon}$. We may assume without loss of generality that $u \in C_0^{\infty}(\Omega)$, since $C_0^{\infty}(\Omega)$ is dense in $H_0^k(\Omega)$ and $\|T_{P,\varepsilon}u - u\|_P^2$ is continuous with respect to $\|\cdot\|_{H_0^k}$. Since $u$ is smooth, for every $x,z \in \Omega$, we have the $k$th-order Taylor expansion
\begin{equation*}
u(z) - u(x) = \sum_{j = 1}^{k - 1} (z - x)^{j} u^{(j)}(x)  + \frac{(z - x)^k}{(k - 1)!}\int_{0}^{1}(1 - t)^{k - 1}u^{(k)}(x + t(z - x))\,dt.
\end{equation*}
As a result,
\begin{equation}
\label{pf:kernel_smoothing_bias_1d_1}
\begin{aligned}
L_{P,\varepsilon}u(x) = \frac{1}{d_P(x)} & \Biggl\{\sum_{j = 1}^{k - 1} u^{(j)}(x) \int_{\Omega}(z - x)^{j}\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr)\,dz + \\ 
& \frac{1}{(k - 1)!} \int_{\Omega} \int_{0}^{1} (1 - t)^k (z - x)^k u^{(k)}(x + t(z - x)) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dt \,dz \Biggr\}
\end{aligned}
\end{equation}

Now, since $x \in \Omega_{\varepsilon}$ then all $z \in B(x,\varepsilon)$ also belong to $\Omega$. For one thing, this implies
\begin{equation*}
d_P(x) = \int_{\Omega} \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz = \varepsilon \cdot \int_{B(0,1)}  \eta(v) \,dv = \epsilon.
\end{equation*}
Additionally, we have that all $j = 1,\ldots,k - 1$, 
\begin{equation*}
\int_{\Omega}(z - x)^{k}\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz = \varepsilon^j \cdot \int_{B(0,1)} v^j \eta(v) \,dv = 0,
\end{equation*}
where the second equality follows because $\eta$ is a $k$th-order kernel. Consequently $L_{P,\varepsilon}$ depends only on the $k$th derivative of $u$: changing variables to $v = (z - x)/\varepsilon$, we have
\begin{align*}
L_{P,\varepsilon}u(x) & = \frac{1}{\varepsilon} \cdot \frac{1}{(k - 1)!} \int_{0}^{1} \int_{\Omega} (1 - t)^k (z - x)^k u^{(k)}(x + t(z - x)) \eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,dz \,dv \\
& = \frac{\varepsilon^{k}}{(k - 1)!} \int_{0}^{1} \int_{B(0,1)} (1 - t)^k v^k u^{(k)}(x + t\varepsilon v) \eta(|v|) \,dv \,dt
\end{align*} 
and as a result
\begin{equation*}
\Bigl(L_{P,\varepsilon}u(x)\Bigr)^2 = \frac{\varepsilon^{2k}}{(k!)^2} {\sigma_\eta}^2 \bigl(u^{(k)}(x)\bigr)^2 + \frac{\varepsilon^{2k}}{((k - 1)!)^2}A_1(x)A_{2}(x),
\end{equation*}
where $\sigma_\eta = \int v^k \eta(|v|) \,dv$ and 
\begin{align*}
A_1(x) & := \int_{0}^{1} \int_{B(0,1)} (1 - t)^k v^k \bigl(u^{(k)}(x + t\varepsilon v) - u^{(k)}(x)\bigr) \eta(|v|) \,dv \,dt \\
A_2(x) & := \int_{0}^{1} \int_{B(0,1)} (1 - t)^k v^k \bigl(u^{(k)}(x + t\varepsilon v) + u^{(k)}(x)\bigr) \eta(|v|) \,dv \,dt.
\end{align*}
Integrating over all $x \in \Omega_{\varepsilon}$, we have that
\begin{align*}
I_1 = \int_{\Omega_{\varepsilon}} \bigl(L_{P,\varepsilon}u(x)\bigr)^2 \,dx & = \frac{\varepsilon^{2k}}{(k!)^2} \sigma_\eta^2 \int_{\Omega_{\varepsilon}} \bigl(u^{(k)}(x)\bigr)^2 \,dx + \frac{\varepsilon^{2k}}{((k - 1)!)^2} \int_{\Omega_{\varepsilon}}A_1(x) A_2(x) \,dx \\
& \leq \frac{\varepsilon^{2k}}{(k!)^2} \Bigl(\sigma_\eta^2 \|u^{(k)}\|_{P}^2 + k^2 \|A_1\|_P \|A_2\|_P\Bigr).
\end{align*}
It remains to show that $\|A_1\|_P\|A_2\|_P = o(1)$.

\textcolor{red}{(TODO): Follow through on this calculation, referring to pages 192 - 195 of Tsybakov's book.}

\paragraph{Upper bound on $I_2$.}
We will prove the upper bound
\begin{equation}
\label{pf:kernel_smoothing_bias_1d_2}
\int_{0}^{\varepsilon} \bigl|L_{P,\varepsilon}u(x)\bigr|^2 \,dx \leq C \varepsilon^{2k + 1}\|u^{(k)}\|_P^2,
\end{equation}
with the bound on $\int_{1 - \varepsilon}^{1} \bigl|L_{P,\varepsilon}u\bigr|^2$ following in a completely analogous fashion.

Unlike the previous case, when $x$ is near the boundary of $\Omega$ we cannot use the higher-order property of $\eta$ to cancel the order-$1$ up through order-$(k - 1)$ derivatives of $u$. Instead, we will use the zero-trace property to show that $u$ itself must be quite small. Taking a Taylor expansion of $u$ around $0$, we have that for any $x \in \Omega$,
\begin{align}
u(x) & = u(0) + \sum_{j = 1}^{k - 1} x^j u^{(j)}(0) + \frac{1}{(k - 1)!} \int_{0}^{x}u^{(k)}(s)(x - s)^{k - 1}\,ds \nonumber \\
& = \frac{1}{(k - 1)!} \int_{0}^{x}u^{(k)}(s)(x - s)^{k - 1}\,ds. \label{pf:kernel_smoothing_bias_1d_3}
\end{align}
with the second inequality following since $u \in C_c^{\infty}(\Omega)$ implies $u(0) = 0$ as well as $u^{(j)}(0) = 0$ for $j = 1,\ldots,k - 1$. To make use of this upper bound on $u(x)$, we upper bound $|L_{P,\varepsilon}u(x)|^2$ using the Cauchy-Schwarz inequality,
\begin{align*}
|L_{P,\varepsilon}u(x)|^2 & = \Biggl(\frac{1}{d_P(x)} \int_{\Omega} \bigl(u(x) - u(z)\bigr) \eta\biggl(\frac{|x - z|}{\varepsilon}\biggr) \,dz\Biggr)^2 \\
& \leq \frac{1}{d_P(x)}\biggl(\int_{\Omega} K^{1/2}\biggl(\frac{x - z}{\varepsilon}\biggr) \,dz\biggr) \cdot \frac{1}{d_P(x)}\int_{\Omega} \bigl(u(x) - u(z)\bigr)^2 K^{1/2}\biggl(\frac{|x - z|}{\varepsilon}\biggr) \,dz \\
& \leq 2\frac{\|\eta\|_{\infty}}{\alpha^2\varepsilon} \cdot \int_{\Omega} \bigl(u(x)^2 + u(z)^2\bigr) K^{1/2}\biggl(\frac{|x - z|}{\varepsilon}\biggr) \,dz,
\end{align*}
where in the final inequality we have used the estimates $d_P(x;K^{1/2}) \leq \|\eta\|_{\infty} \varepsilon$ and $d_P(x) \geq (\varepsilon\alpha)$.

We use these pointwise estimates to upper bound~\eqref{pf:kernel_smoothing_bias_1d_2}. Since $\eta$ is compactly supported, if $x \in (0,\varepsilon]$ and $\eta(|x - z|/\varepsilon) > 0$ then $z \in (0,2\varepsilon]$. As a result,
\begin{align*}
\int_{0}^{\varepsilon} |L_{P,\varepsilon}u(x)|^2 \,dP(x) & \leq 2\frac{\|\eta\|_{\infty}}{\alpha^2\varepsilon} \int_{0}^{\varepsilon}  \int_{\Omega} \bigl(u(x)^2 + u(z)^2\bigr) K^{1/2}\biggl(\frac{|x - z|}{\varepsilon}\biggr) \,dz \,dx \\
& \leq 2\frac{\|\eta\|_{\infty}}{\alpha^2\varepsilon} \int_{0}^{2\varepsilon}  \int_{0}^{2\varepsilon} \bigl(u(x)^2 + u(z)^2\bigr) K^{1/2}\biggl(\frac{|x - z|}{\varepsilon}\biggr) \,dz \,dx \\
& \leq 4\frac{\|\eta\|_{\infty}^2}{\alpha^2} \int_{0}^{2\varepsilon} (u(x))^2 \,dx,
\end{align*}
where the last inequality follows by Fubini's Theorem.

It remains to upper bound the $\Leb^2$ norm of $u$ over $(0,2\varepsilon]$. Here we use the bound~\eqref{pf:kernel_smoothing_bias_1d_3} and the Cauchy-Schwarz inequality to conclude that 
\begin{equation*}
\int_{0}^{2\varepsilon} \bigl(u(x)\bigr)^2 \,dx \leq \int_{0}^{2\varepsilon} \biggl(\int_{0}^{x} u^{(k)}(s)(x - s)^{k - 1} \,ds\biggr)^2 \,dx \leq \varepsilon^{2k - 1} \int_{0}^{2\varepsilon} \int_{0}^{x} \bigl(u^{(k)}(s)\bigr)^2 \,ds \,dx. 
\end{equation*}
Finally, switching the order of integration and substituting $v = s/(2\varepsilon)$ gives
\begin{align*}
\int_{0}^{2\varepsilon} \int_{0}^{x} \bigl(u^{(k)}(s)\bigr)^2 \,ds \,dx = \int_{0}^{2\varepsilon} \int_{x}^{2\varepsilon} \bigl(u^{(k)}(s)\bigr)^2 \,dx \,ds \leq 2\varepsilon \int_{0}^{2\varepsilon} \bigl(u^{(k)}(s)\bigr)^2 \,ds = 4\varepsilon^2 \|u^{(k)}\|_P^2,
\end{align*}
establishing~\eqref{pf:kernel_smoothing_bias_1d_2} upon choosing $C = \frac{16\|\eta\|_{\infty}^2}{\alpha^2}$ in the statement of the inequality.

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_bias}, $d = 1$ and $p \in C^k$.}
\label{subsec:kernel_smoothing_bias_pf_1d_smooth_p}
As in~\ref{subsec:kernel_smoothing_bias_pf_1d_uniform_p}, we take $\Omega = (0,1)$, let
\begin{equation*}
\|L_{P,\varepsilon}u\|_{P}^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2},
\end{equation*}
and turn to separately upper bounding $I_1$ and $I_2$.
